Breeding bird indicators

### 2023-11-14 Connectivity.Rmd

---
title: "Template for indicator documentation"
output:
  html_document
---

<!-- This is a template for how to document the indicator analyses.

Make a copy of this file and store it in the root folder (same as where this template is stored) folder. 
Name the file DRAFT_myIndicatorName.Rmd.

Because this is a stand-alone Rmd file inside a bookdown project, in order to knit the file for preview purposes,
you need to type rmarkdown::render("template.Rmd") in the console, 
as the the usual Ctrl + Alt + k will not work.

Make sure also to not change the order, or modify the headers, unless you really need to. This is because it
easier to read the web page as a whole of the indicators are presented using the same layout.

When the analyses is complete, Anders Kolstad, or someone else, will perform a rapid code review, making sure 
the analysis is repeatable by someone else. Be therefore very careful to annotate 
and comment on every step in the analysis. When completed, Anders will make a copy
of the working file and put it in the same project root folder, but removing the 'DRAFT_' part of the name. 
After modifying it slightly (mainly removing the top YAML header and updating the rmd_files argument in '_bookdown.yml') 
the output will become available on the website (https://ninanor.github.io/ecosystemCondition/). -->

<!-- Examples:

For an example, see 'indicators/breareal-workingFile.Rmd' 
and the subsequent 'breareal.Rmd' 
which again, when rendered, produces this:
https://ninanor.github.io/ecosystemCondition/areal-av-isbreer.html

Notice the degree of annotation.

-->

<!-- Replace 'indicator name' with yor own indicator name  -->
# Connectivity

@@

October 2023

@@

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

@@

Here a general workflow for the calculation of the indicator.

1.	You must load the necessary libraries for geospatial analysis.
2.	You must load the infrastructure index and wetland data.
3.	You define the buffer distance (500 meters).
4.	You must create a function (``calculateMeanDistance``) to calculate the mean distance to infrastructure within a buffer around each wetland polygon.
5.	Then you filter and keep only the homogeneous wetlands with more than 80% mire coverage.
6.	You have to apply the ``calculateMeanDistance`` function to these selected wetlands, both with and without infrastructure.
7.	You export the results as shapefiles for both scenarios.
8.	The scaled values for the "Connectivity" indicator are determined by comparing two scenarios: one that includes the presence of infrastructure and one that excludes infrastructure. The reference value is calculated as the ratio of the mean distances between myrpolygon areas in these two scenarios.

Currently step 8, and a subsequent step 9 (to aggregate scaled indicators to regions and simultaneously calculate errors) are not complete. Se [this issue]()https://github.com/NINAnor/ecosystemCondition/issues/144.

It is also possible to create a time series for this indicator, but this is not yet done. See [GitHub issue](https://github.com/NINAnor/ecosystemCondition/issues/145).

## About the underlying data {#underlying-data-con}
The **infrastructure index** is one part of the connectivity index for wetlands. The infrastructure index was calculated for three time points: 2003, 2013, and 2023. This provides a temporal perspective for assessing changes over time. The data used included information on various types of infrastructure, such as roads and buildings. Additionally, a **new wetland** map for Norway has been developed. This map is based on Sentinel-2 and LiDAR data from the year 2020. The U-Net model, implemented through Google Earth Engine and TensorFlow, has been used for mapping wetlands in southern Norway. The model achieved a balanced accuracy rate of 90.9% when validated against ground-truth samples, significantly improving upon the accuracy rates achieved with manually digitized maps in Norway.

### Representativity in time and space {#representativity-con}
The data for the infrastructure index covers the entire country and was collected for three time points over a 20-year period. This provides a broad and representative dataset for assessing changes in connectivity in Norwegian landscapes. The wetland mapping was conducted using data from the year 2020, making it representative for that specific time frame. However, the model used in the mapping process can be applied to other time frames if necessary.

### Original units {#units-con}
The infrastructure index has no specific units as it is a measure of landscape fragmentation and disruption. It is expressed as a dimensionless index.

### Temporal coverage {#temporal-coverage-con}
The data covers three time points: 2003, 2013, and 2023. This provides a 20-year temporal perspective for assessing changes in connectivity over time. The wetland mapping provides information in the form of pixel values representing wetland presence or absence.

### Aditional comments about the dataset {#additional-comments-con}
It is important to note that infrastructure data are based on available map and geographical data sources. Sometimes, there may be variations and uncertainties in this data that can affect the accuracy of the infrastructure index.

## Ecosystem characteristic {#egenskap-con}
In the context of the Norwegian standard, the "Connectivity" indicator aligns with the ecosystem characteristic known as **Landskapsøkologiske mønstre**.

### SEEA EA (UN standard) {#seea-con}
In the framework of the United Nations System of Environmental-Economic Accounting (SEEA EA), the _Connectivity_ indicator can be classified as a **C1 Landscape and seascape characteristics** indicator.

## Collinearities with other indicators {#collinear-con}
Connectivity is not thought to exhibit collinearity with any other indicator at the present.

## Reference condition and values {#ref-conditions-and-values-con}
### Reference condition {#ref-condition-con}
The reference condition for the "Connectivity" indicator is characterized as one with minimal negative human impact on the connectivity of ecosystems. In this reference condition, the landscape exhibits natural and undisturbed patterns of connectivity between suitable habitats. This state represents the optimal ecological condition for connectivity assessment.

### Reference values, thresholds for defining _good ecological condition_, minimum and/or maximum values {#ref-values-con}
The reference values for the "Connectivity" indicator are determined by calculating the connectivity or mean distance to mire polygons, when excluding infrastructure from the analysis.

In the report «Vurdering av økologisk tilstand for fjell i Norge i 2021» (Framstad et al. 2021) the value of 0,6 was used as the threshold for good ecological condition. We will tentatively use this threshold value again here. A perpetual discussion about the reference (and threshold values) for the connectivity indicator is maintained on [GitHub.](https://github.com/NINAnor/ecosystemCondition/issues/143)

## Uncertainties {#uncertainties-con}
Our wetland mapping model is a powerful tool for large-scale mapping but does come with certain uncertainties. While our U-Net model achieved an impressive balanced accuracy rate of 90.9% when validated against an independent ground-truth sample, it's essential to recognize that some level of uncertainty is inherent. The model's accuracy may vary across different wetland types and landscape conditions. The model's performance might vary in regions with distinct wetland characteristics that differ from our training data. It may not fully capture variations in wetland types or subtle differences in wetland boundaries. The accuracy of the wetland mapping model is influenced by the quality and representativeness of the training data. We made significant efforts to ensure the highest quality, but the inherent variability in ground-truth data may introduce some level of uncertainty.

The infrastructure data sources used for this analysis might contain inaccuracies, errors, or omissions. These can arise from factors like inconsistent reporting and data collection methods. While infrastructure data is a valuable proxy for landscape barriers, it may not capture all potential barriers accurately. For instance, small-scale features or unreported structures could introduce uncertainties in connectivity assessments. The resolution of the infrastructure data might not capture all relevant features at a fine scale. This can affect the precision of connectivity assessments in areas with small, localized infrastructure.

## References
Bakkestuen, V.; Venter, Z.; Ganerød, A.J.; Framstad, E. Delineation of Wetland Areas in South Norway from Sentinel-2 Imagery and LiDAR Using TensorFlow, U-Net, and Google Earth Engine. Remote Sens. 2023, 15, 1203. https://doi.org/10.3390/rs15051203

Bakkestuen, V. et al. in prep. Comprehensive Mapping of Wetland Areas in Norway: An Integration of Sentinel-2 Imagery, LiDAR, and Deep Learning Using TensorFlow and Google Earth Engine

Erikstad, L.; Simensen, T.; Bakkestuen, V.; Halvorsen, R. Index Measuring Land Use Intensity—A Gradient-Based Approach. Geomatics 2023, 3, 188-204. https://doi.org/10.3390/geomatics3010010

Framstad, E., Eide, N.E., Eide, W., Klanderud, K., Kolstad, A., Töpper, J. & Vandvik, V. 2022. Vurdering av økologisk tilstand for fjell i Norge i 2021. NINA Rapport 2050. Norsk institutt for naturforskning.

Husk en refERANSE TIL KKLG

## Analyses {#analyses-con}
### Data sets {#datasets-con}
Two main data sets were included.

A. The infrastructure index (Erikstad et al. 2023) and;

B. the wetland model (Bakkestuen et al. 2023, Bakkestuen et al. _In prep._)

#### Data set A - Infrastructure index {#data-a-con}
The infrastructure index utilized in this analysis was derived from data sources available through Google Earth Engine (GEE). The index quantifies the presence and distribution of key infrastructure elements such as roads, buildings, and related human-made structures across Norway. The data were available for the years 2003, 2013, and 2023, facilitating an assessment of how infrastructure has evolved in terms of both magnitude and distribution over time. It is important to note that this data forms a fundamental component in the calculation of the connectivity indicator.

#### Data set B - Wetland model {#data-b-con}
The wetland model used in this study was developed based on the integration of Sentinel-2 satellite imagery and LiDAR data, utilizing deep learning techniques. The model provides high-resolution information regarding the distribution and extent of wetland areas within southern Norway, specifically for the year 2020. By fusing spectral and elevation data, this model offers significant improvements over conventional, manually-digitized land cover maps. The wetland model is a critical component of the connectivity analysis, as it aids in the identification of ecologically relevant areas. The data set B for South-Norway is already accessible [here](https://kartkatalog.geonorge.no/metadata/aapen-vtmark-i-soer-norge-basert-p-natur-i-norge-nin-typologi/6b5a34f9-c23d-4cca-a51b-01251c217cb1).

### Scaled indicator values {#scaled-values-con}
The connectivity indicator was created by examining the interplay between infrastructure and wetland areas. We initially calculated the average distance between wetland patches using the wetland model, representing a baseline measure of natural connectivity in the absence of infrastructure (i.e., the reference condition). Subsequently, the infrastructure index was introduced, portraying the extent of human-made structural elements within the landscape.
The scaled indicator is the quotient of the values.

### Uncertainty {#uncertainty-con}
The current state of the indicator is as a geospatial data set with one scaled indicator value per mire polygon, and no errors around this value. Future improvement must include aggregating these indicator values to regions. The uncertainties around these aggregated indicator values could then be represented by the spatial variation in the indicator values.

## Prepare export {#pre-export-con}
You must run the whole code below. There is a maximum of 5000 wetland polygons for each export.

### JAVA code {#java-con}

Koden er utviklet i JAVA for Google Earth Engine:

```{}
// Senter kartet til en bestemt geografisk posisjon (bredde- og lengdegrad) og velg en zoomnivå
Map.setCenter(11.0534047, 62.14137, 12);

// Laste inn infrastrukturindeks og myr datasett fra Google Earth Engine Data
var infrastruktur = ee.Image('users/vegar/NY_INFRA_IND');
var myrpred2 = ee.ImageCollection('users/vegarbakkestuen/Myr153');
var myr = myrpred2.mean();

// Legg til myrdata som et lag på kartet med tilpassede visningsparametere
Map.addLayer(myr, { min: 0, max: 1, palette: ['white', 'green'] }, 'myr');
Map.addLayer(infrastruktur, { min: 0, max: 13, palette: ['blue', 'yellow', 'red'] }, 'infrastruktur');

// Definer en bufferavstand (i meter) som bestemmer området som blir analysert rundt hvert myrpolygon
var bufferDistance = 500;

// Funksjon for å beregne gjennomsnittlig avstand til infrastruktur basert på grenseverdien
var calculateMeanDistance = function (feature) {
  var threshold = 3;  // Definer din grenseverdi for infrastruktur

  // Filtrer infrastrukturbildet basert på grenseverdien
  var filteredInfrastructure = infrastruktur.gt(threshold);

  // Hent myrpolygonets sentrum
  var myrCenter = feature.geometry().centroid(100);

  // Beregn gjennomsnittlig avstand til infrastruktur ved å redusere regionen rundt hvert myrpolygon
  var distanceWithInfrastructure = filteredInfrastructure.rename('filtered_infra').reduceRegion({
    reducer: ee.Reducer.mean(),
    geometry: feature.geometry().buffer(bufferDistance),
    scale: 10,  // Oppløsningen til datasettet (meters per piksel)
    maxPixels: 1e13
  }).get('filtered_infra');

  var distanceWithoutInfrastructure = filteredInfrastructure.rename('filtered_infra').reduceRegion({
    reducer: ee.Reducer.mean(),
    geometry: myrCenter.buffer(bufferDistance),
    scale: 10,  // Oppløsningen til datasettet (meters per piksel)
    maxPixels: 1e13
  }).get('filtered_infra');

  // Skalér brøkverdien til meter ved å multiplisere med bufferavstanden
  var scaledDistanceWithInfrastructure = ee.Number(distanceWithInfrastructure).multiply(bufferDistance);
  var scaledDistanceWithoutInfrastructure = ee.Number(distanceWithoutInfrastructure).multiply(bufferDistance);

  // Beregn kvotienten (forholdet mellom avstand uten infrastruktur og avstand med infrastruktur)
  var kvotient = scaledDistanceWithoutInfrastructure.divide(scaledDistanceWithInfrastructure);

  var properties = {
    'distinfra_meters': scaledDistanceWithInfrastructure,
    'distnoinfra_meters': scaledDistanceWithoutInfrastructure,
    'kvotient': kvotient
  };

  return feature.set(properties);
};

// Velg områder med myr (myrinnhold > 80%) og bruk dette som geometri for analysen
var omraderMedMyr = myr.gt(0.8).selfMask();

// Hent geometriene for hvert område med myr
var omraderGeometries = omraderMedMyr.reduceToVectors({
  geometry: geometry,
  scale: 10,  // Oppløsningen til datasettet (meters per piksel)
  maxPixels: 1e13
});

// Bruk funksjonen calculateMeanDistance for å beregne gjennomsnittlig avstand til infrastruktur for hvert område med myr
var omraderMedGjennomsnittligAvstand = omraderGeometries.map(calculateMeanDistance);

// Legg til lag som viser myrpolygonene og lag med gjennomsnittlig avstand til infrastruktur på kartet
Map.addLayer(omraderMedMyr, { min: 0, max: 1, palette: ['white', 'green'] }, 'Myrpolygoner');

// Vis scenariet "Konnektivitet med infrastruktur" på kartet
var visParams = {
  min: 0,
  max: 1, // Juster dette basert på din infrastrukturindeksens min og maks
  palette: ['blue', 'yellow', 'red'],
};
Map.addLayer(omraderMedGjennomsnittligAvstand, visParams, 'Gjennomsnittlig avstand til infrastruktur');

// Eksporter resultatene som en Shapefile til Google Drive
Export.table.toDrive({
  collection: omraderMedGjennomsnittligAvstand,
  description: 'Konnektivitet_med_infrastruktur',
  fileFormat: 'SHP',
});

```

The scaled "Connectivity" values are created by dividing the result without infrastructure by the result that includes infrastructure. This ratio will give you a value between 0 and 1, where 0 represents complete disruption of connectivity due to infrastructure, and 1 represents undisturbed natural connectivity.

This step is not yet done, but in R this is how one would do it.
Calculate the reference value for connectivity
```{r, eval=FALSE}
reference_value <- selected_wetlands_without_infrastructure$mean_distance / selected_wetlands_with_infrastructure$mean_distance
```

>>>>

# Connectivity

@@

November 2023

@@

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(flextable)
```

@@

> MORE INFO COMING SOON!

<!-- Here a general workflow for the calculation of the indicator. -->

<!-- 1.	You must load the necessary libraries for geospatial analysis. -->
<!-- 2.	You must load the infrastructure index and wetland data. -->
<!-- 3.	You define the buffer distance (500 meters). -->
<!-- 4.	You must create a function (``calculateMeanDistance``) to calculate the mean distance to infrastructure within a buffer around each wetland polygon. -->
<!-- 5.	Then you filter and keep only the homogeneous wetlands with more than 80% mire coverage. -->
<!-- 6.	You have to apply the ``calculateMeanDistance`` function to these selected wetlands, both with and without infrastructure. -->
<!-- 7.	You export the results as shapefiles for both scenarios. -->
<!-- 8.	The scaled values for the "Connectivity" indicator are determined by comparing two scenarios: one that includes the presence of infrastructure and one that excludes infrastructure. The reference value is calculated as the ratio of the mean distances between myrpolygon areas in these two scenarios. -->

<!-- Currently step 8, and a subsequent step 9 (to aggregate scaled indicators to regions and simultaneously calculate errors) are not complete. Se [this issue]()https://github.com/NINAnor/ecosystemCondition/issues/144. -->

<!-- It is also possible to create a time series for this indicator, but this is not yet done. See [GitHub issue](https://github.com/NINAnor/ecosystemCondition/issues/145). -->

<!-- ## About the underlying data {#underlying-data-con} -->
<!-- The **infrastructure index** is one part of the connectivity index for wetlands. The infrastructure index was calculated for three time points: 2003, 2013, and 2023. This provides a temporal perspective for assessing changes over time. The data used included information on various types of infrastructure, such as roads and buildings. Additionally, a **new wetland** map for Norway has been developed. This map is based on Sentinel-2 and LiDAR data from the year 2020. The U-Net model, implemented through Google Earth Engine and TensorFlow, has been used for mapping wetlands in southern Norway. The model achieved a balanced accuracy rate of 90.9% when validated against ground-truth samples, significantly improving upon the accuracy rates achieved with manually digitized maps in Norway. -->

<!-- ### Representativity in time and space {#representativity-con} -->
<!-- The data for the infrastructure index covers the entire country and was collected for three time points over a 20-year period. This provides a broad and representative dataset for assessing changes in connectivity in Norwegian landscapes. The wetland mapping was conducted using data from the year 2020, making it representative for that specific time frame. However, the model used in the mapping process can be applied to other time frames if necessary. -->

<!-- ### Original units {#units-con} -->
<!-- The infrastructure index has no specific units as it is a measure of landscape fragmentation and disruption. It is expressed as a dimensionless index. -->

<!-- ### Temporal coverage {#temporal-coverage-con} -->
<!-- The data covers three time points: 2003, 2013, and 2023. This provides a 20-year temporal perspective for assessing changes in connectivity over time. The wetland mapping provides information in the form of pixel values representing wetland presence or absence. -->

<!-- ### Aditional comments about the dataset {#additional-comments-con} -->
<!-- It is important to note that infrastructure data are based on available map and geographical data sources. Sometimes, there may be variations and uncertainties in this data that can affect the accuracy of the infrastructure index. -->

<!-- ## Ecosystem characteristic {#egenskap-con} -->
<!-- In the context of the Norwegian standard, the "Connectivity" indicator aligns with the ecosystem characteristic known as **Landskapsøkologiske mønstre**. -->

<!-- ### SEEA EA (UN standard) {#seea-con} -->
<!-- In the framework of the United Nations System of Environmental-Economic Accounting (SEEA EA), the _Connectivity_ indicator can be classified as a **C1 Landscape and seascape characteristics** indicator. -->

<!-- ## Collinearities with other indicators {#collinear-con} -->
<!-- Connectivity is not thought to exhibit collinearity with any other indicator at the present. -->

<!-- ## Reference condition and values {#ref-conditions-and-values-con} -->
<!-- ### Reference condition {#ref-condition-con} -->
<!-- The reference condition for the "Connectivity" indicator is characterized as one with minimal negative human impact on the connectivity of ecosystems. In this reference condition, the landscape exhibits natural and undisturbed patterns of connectivity between suitable habitats. This state represents the optimal ecological condition for connectivity assessment. -->

<!-- ### Reference values, thresholds for defining _good ecological condition_, minimum and/or maximum values {#ref-values-con} -->
<!-- The reference values for the "Connectivity" indicator are determined by calculating the connectivity or mean distance to mire polygons, when excluding infrastructure from the analysis. -->

<!-- In the report «Vurdering av økologisk tilstand for fjell i Norge i 2021» (Framstad et al. 2021) the value of 0,6 was used as the threshold for good ecological condition. We will tentatively use this threshold value again here. A perpetual discussion about the reference (and threshold values) for the connectivity indicator is maintained on [GitHub.](https://github.com/NINAnor/ecosystemCondition/issues/143) -->

<!-- ## Uncertainties {#uncertainties-con} -->
<!-- Our wetland mapping model is a powerful tool for large-scale mapping but does come with certain uncertainties. While our U-Net model achieved an impressive balanced accuracy rate of 90.9% when validated against an independent ground-truth sample, it's essential to recognize that some level of uncertainty is inherent. The model's accuracy may vary across different wetland types and landscape conditions. The model's performance might vary in regions with distinct wetland characteristics that differ from our training data. It may not fully capture variations in wetland types or subtle differences in wetland boundaries. The accuracy of the wetland mapping model is influenced by the quality and representativeness of the training data. We made significant efforts to ensure the highest quality, but the inherent variability in ground-truth data may introduce some level of uncertainty. -->

<!-- The infrastructure data sources used for this analysis might contain inaccuracies, errors, or omissions. These can arise from factors like inconsistent reporting and data collection methods. While infrastructure data is a valuable proxy for landscape barriers, it may not capture all potential barriers accurately. For instance, small-scale features or unreported structures could introduce uncertainties in connectivity assessments. The resolution of the infrastructure data might not capture all relevant features at a fine scale. This can affect the precision of connectivity assessments in areas with small, localized infrastructure. -->

<!-- ## References -->
<!-- Bakkestuen, V.; Venter, Z.; Ganerød, A.J.; Framstad, E. Delineation of Wetland Areas in South Norway from Sentinel-2 Imagery and LiDAR Using TensorFlow, U-Net, and Google Earth Engine. Remote Sens. 2023, 15, 1203. https://doi.org/10.3390/rs15051203 -->

<!-- Bakkestuen, V. et al. in prep. Comprehensive Mapping of Wetland Areas in Norway: An Integration of Sentinel-2 Imagery, LiDAR, and Deep Learning Using TensorFlow and Google Earth Engine -->

<!-- Erikstad, L.; Simensen, T.; Bakkestuen, V.; Halvorsen, R. Index Measuring Land Use Intensity—A Gradient-Based Approach. Geomatics 2023, 3, 188-204. https://doi.org/10.3390/geomatics3010010 -->

<!-- Framstad, E., Eide, N.E., Eide, W., Klanderud, K., Kolstad, A., Töpper, J. & Vandvik, V. 2022. Vurdering av økologisk tilstand for fjell i Norge i 2021. NINA Rapport 2050. Norsk institutt for naturforskning. -->

<!-- Husk en refERANSE TIL KKLG -->

<!-- ## Analyses {#analyses-con} -->
<!-- ### Data sets {#datasets-con} -->
<!-- Two main data sets were included. -->

<!-- A. The infrastructure index (Erikstad et al. 2023) and; -->

<!-- B. the wetland model (Bakkestuen et al. 2023, Bakkestuen et al. _In prep._) -->

<!-- #### Data set A - Infrastructure index {#data-a-con} -->
<!-- The infrastructure index utilized in this analysis was derived from data sources available through Google Earth Engine (GEE). The index quantifies the presence and distribution of key infrastructure elements such as roads, buildings, and related human-made structures across Norway. The data were available for the years 2003, 2013, and 2023, facilitating an assessment of how infrastructure has evolved in terms of both magnitude and distribution over time. It is important to note that this data forms a fundamental component in the calculation of the connectivity indicator. -->

<!-- #### Data set B - Wetland model {#data-b-con} -->
<!-- The wetland model used in this study was developed based on the integration of Sentinel-2 satellite imagery and LiDAR data, utilizing deep learning techniques. The model provides high-resolution information regarding the distribution and extent of wetland areas within southern Norway, specifically for the year 2020. By fusing spectral and elevation data, this model offers significant improvements over conventional, manually-digitized land cover maps. The wetland model is a critical component of the connectivity analysis, as it aids in the identification of ecologically relevant areas. The data set B for South-Norway is already accessible [here](https://kartkatalog.geonorge.no/metadata/aapen-vtmark-i-soer-norge-basert-p-natur-i-norge-nin-typologi/6b5a34f9-c23d-4cca-a51b-01251c217cb1). -->

<!-- ### Scaled indicator values {#scaled-values-con} -->
<!-- The connectivity indicator was created by examining the interplay between infrastructure and wetland areas. We initially calculated the average distance between wetland patches using the wetland model, representing a baseline measure of natural connectivity in the absence of infrastructure (i.e., the reference condition). Subsequently, the infrastructure index was introduced, portraying the extent of human-made structural elements within the landscape. -->
<!-- The scaled indicator is the quotient of the values. -->

<!-- ### Uncertainty {#uncertainty-con} -->
<!-- The current state of the indicator is as a geospatial data set with one scaled indicator value per mire polygon, and no errors around this value. Future improvement must include aggregating these indicator values to regions. The uncertainties around these aggregated indicator values could then be represented by the spatial variation in the indicator values. -->

<!-- ## Prepare export {#pre-export-con} -->
<!-- You must run the whole code below. There is a maximum of 5000 wetland polygons for each export. -->

<!-- ### JAVA code {#java-con} -->

<!-- Koden er utviklet i JAVA for Google Earth Engine: -->

<!-- ```{} -->
<!-- // Senter kartet til en bestemt geografisk posisjon (bredde- og lengdegrad) og velg en zoomnivå -->
<!-- Map.setCenter(11.0534047, 62.14137, 12); -->

<!-- // Laste inn infrastrukturindeks og myr datasett fra Google Earth Engine Data -->
<!-- var infrastruktur = ee.Image('users/vegar/NY_INFRA_IND'); -->
<!-- var myrpred2 = ee.ImageCollection('users/vegarbakkestuen/Myr153'); -->
<!-- var myr = myrpred2.mean(); -->

<!-- // Legg til myrdata som et lag på kartet med tilpassede visningsparametere -->
<!-- Map.addLayer(myr, { min: 0, max: 1, palette: ['white', 'green'] }, 'myr'); -->
<!-- Map.addLayer(infrastruktur, { min: 0, max: 13, palette: ['blue', 'yellow', 'red'] }, 'infrastruktur'); -->

<!-- // Definer en bufferavstand (i meter) som bestemmer området som blir analysert rundt hvert myrpolygon -->
<!-- var bufferDistance = 500; -->

<!-- // Funksjon for å beregne gjennomsnittlig avstand til infrastruktur basert på grenseverdien -->
<!-- var calculateMeanDistance = function (feature) { -->
<!--   var threshold = 3;  // Definer din grenseverdi for infrastruktur -->

<!--   // Filtrer infrastrukturbildet basert på grenseverdien -->
<!--   var filteredInfrastructure = infrastruktur.gt(threshold); -->

<!--   // Hent myrpolygonets sentrum -->
<!--   var myrCenter = feature.geometry().centroid(100); -->

<!--   // Beregn gjennomsnittlig avstand til infrastruktur ved å redusere regionen rundt hvert myrpolygon -->
<!--   var distanceWithInfrastructure = filteredInfrastructure.rename('filtered_infra').reduceRegion({ -->
<!--     reducer: ee.Reducer.mean(), -->
<!--     geometry: feature.geometry().buffer(bufferDistance), -->
<!--     scale: 10,  // Oppløsningen til datasettet (meters per piksel) -->
<!--     maxPixels: 1e13 -->
<!--   }).get('filtered_infra'); -->

<!--   var distanceWithoutInfrastructure = filteredInfrastructure.rename('filtered_infra').reduceRegion({ -->
<!--     reducer: ee.Reducer.mean(), -->
<!--     geometry: myrCenter.buffer(bufferDistance), -->
<!--     scale: 10,  // Oppløsningen til datasettet (meters per piksel) -->
<!--     maxPixels: 1e13 -->
<!--   }).get('filtered_infra'); -->

<!--   // Skalér brøkverdien til meter ved å multiplisere med bufferavstanden -->
<!--   var scaledDistanceWithInfrastructure = ee.Number(distanceWithInfrastructure).multiply(bufferDistance); -->
<!--   var scaledDistanceWithoutInfrastructure = ee.Number(distanceWithoutInfrastructure).multiply(bufferDistance); -->

<!--   // Beregn kvotienten (forholdet mellom avstand uten infrastruktur og avstand med infrastruktur) -->
<!--   var kvotient = scaledDistanceWithoutInfrastructure.divide(scaledDistanceWithInfrastructure); -->

<!--   var properties = { -->
<!--     'distinfra_meters': scaledDistanceWithInfrastructure, -->
<!--     'distnoinfra_meters': scaledDistanceWithoutInfrastructure, -->
<!--     'kvotient': kvotient -->
<!--   }; -->

<!--   return feature.set(properties); -->
<!-- }; -->

<!-- // Velg områder med myr (myrinnhold > 80%) og bruk dette som geometri for analysen -->
<!-- var omraderMedMyr = myr.gt(0.8).selfMask(); -->

<!-- // Hent geometriene for hvert område med myr -->
<!-- var omraderGeometries = omraderMedMyr.reduceToVectors({ -->
<!--   geometry: geometry, -->
<!--   scale: 10,  // Oppløsningen til datasettet (meters per piksel) -->
<!--   maxPixels: 1e13 -->
<!-- }); -->

<!-- // Bruk funksjonen calculateMeanDistance for å beregne gjennomsnittlig avstand til infrastruktur for hvert område med myr -->
<!-- var omraderMedGjennomsnittligAvstand = omraderGeometries.map(calculateMeanDistance); -->

<!-- // Legg til lag som viser myrpolygonene og lag med gjennomsnittlig avstand til infrastruktur på kartet -->
<!-- Map.addLayer(omraderMedMyr, { min: 0, max: 1, palette: ['white', 'green'] }, 'Myrpolygoner'); -->

<!-- // Vis scenariet "Konnektivitet med infrastruktur" på kartet -->
<!-- var visParams = { -->
<!--   min: 0, -->
<!--   max: 1, // Juster dette basert på din infrastrukturindeksens min og maks -->
<!--   palette: ['blue', 'yellow', 'red'], -->
<!-- }; -->
<!-- Map.addLayer(omraderMedGjennomsnittligAvstand, visParams, 'Gjennomsnittlig avstand til infrastruktur'); -->

<!-- // Eksporter resultatene som en Shapefile til Google Drive -->
<!-- Export.table.toDrive({ -->
<!--   collection: omraderMedGjennomsnittligAvstand, -->
<!--   description: 'Konnektivitet_med_infrastruktur', -->
<!--   fileFormat: 'SHP', -->
<!-- }); -->

<!-- ``` -->

<!-- The scaled "Connectivity" values are created by dividing the result without infrastructure by the result that includes infrastructure. This ratio will give you a value between 0 and 1, where 0 represents complete disruption of connectivity due to infrastructure, and 1 represents undisturbed natural connectivity. -->

<!-- This step is not yet done, but in R this is how one would do it. -->
<!-- Calculate the reference value for connectivity -->
<!-- ```{r, eval=FALSE} -->
<!-- reference_value <- selected_wetlands_without_infrastructure$mean_distance / selected_wetlands_with_infrastructure$mean_distance -->
<!-- ``` -->
